\documentclass{article}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}

\title{\textbf{Pepeheavyhash: An Innovative Memecoin on the Kaspa Network}}
\author{Pepeheavy @pepeheavy}
\date{June 21, 2024}

\begin{document}
\maketitle

\begin{abstract}
Pepeheavyhash is an innovative and unique memecoin launched on the Kaspa network, designed to showcase the capabilities of the KRC20 token protocol. Built on the groundbreaking GhostDAG data structure, this project aims to highlight the achievements of the Kasplex team while redefining the narrative around memecoins. Inspired by the popular internet meme Pepe the Frog, Pepeheavyhash re-imagines the character as an older, wiser grandpa with a gray beard, embodying energy, spirituality, and strength. This research paper explores the key features, goals, and tokenomics of Pepeheavyhash, as well as its potential impact on the Kaspa ecosystem and the broader cryptocurrency community.
\end{abstract}

\section{Introduction}
Memecoins have gained significant popularity in the cryptocurrency space, often serving as a lighthearted and entertaining way to engage with blockchain technology \citep{chohan2021rise}. However, Pepeheavyhash aims to go beyond mere entertainment by showcasing the capabilities of the Kaspa network and its innovative GhostDAG consensus mechanism \citep{sompolinsky2020phantom}.

\section{Key Features}
\begin{itemize}
    \item \textbf{Fair Launch}: No pre-allocation, no presale, and no taxes, ensuring a fair and decentralized distribution of tokens \citep{fairlaunch2023}.
    \item \textbf{Community Funded}: Entirely supported by the community, aligning with the principles of decentralization and community governance \citep{defi2022}.
    \item \textbf{Launch Timeline}: Scheduled for the end of June 2024 or early July 2024, pending the activation of the KRC20 protocol on the Kaspa Mainnet \citep{kaspadev2024}.
\end{itemize}

\section{About Pepeheavyhash}
Pepeheavyhash is more than just a memecoin; it is a testament to the potential of the Kaspa network and its innovative GhostDAG consensus algorithm \citep{sompolinsky2020phantom}. With the upcoming launch of the Kasplex protocol and KRC20 Tokens, Pepeheavyhash aims to set a new standard for memecoins on Kaspa, showcasing the capabilities of this cutting-edge technology.

\subsection{Character Inspiration}
Pepeheavyhash is inspired by Pepe the Frog, a popular internet meme \citep{pepe2021}, but with a unique twist. This version of Pepe is depicted as an older, wiser grandpa with a gray beard. He embodies energy, spirituality, and strength, being a non-meat eater who regularly works out at the gym. This distinctive character adds a fresh narrative to the KRC20 memecoin space, combining humor and cultural relevance with a focus on health and wellness.

\subsection{Project Goals}
\begin{enumerate}
    \item \textbf{Showcase Kaspa Network}: Demonstrate the capabilities of the Kaspa network and its groundbreaking GhostDAG consensus mechanism through the use of KRC20 tokens, highlighting the scalability, efficiency, and security of this innovative technology \citep{sompolinsky2020phantom}.
    \item \textbf{Inspire Innovation}: Encourage other communities to develop new projects, such as KRC20 Stablecoins, or to migrate ERC20 tokens to Kaspa to reduce gas costs and benefit from the scalability and efficiency of the GhostDAG consensus mechanism \citep{kaspadev2024}.
    \item \textbf{Set a Benchmark}: Establish a new standard for memecoins on Kaspa, paving the way for future projects and showcasing the potential of the network, while also promoting a positive message of health and wellness \citep{cryptowellness2023}.
\end{enumerate}

\section{Tokenomics}

Pepeheavyhash (PEPEH) employs a carefully designed tokenomics model that leverages the innovative features of the Kaspa network and its GhostDAG consensus mechanism. This model aims to ensure fair distribution, promote community engagement, and support long-term sustainability of the project.

\subsection{Token Details}

\begin{table}[h]
\centering
\begin{tabular}{|l|l|}
\hline
\textbf{Parameter} & \textbf{Value} \\
\hline
Ticker & PEPEH \\
Protocol & KRC20 on Kaspa Network \\
Total Supply & 21,000,000,000 (21 Billion) \\
Per Mint Limit & 1,000 PEPEH \\
Maximum Mints & 10,000,000 \\
Initial Market Cap & 10,500,000,000 PEPEH \\
Decimal Places & 18 \\
Consensus Mechanism & GhostDAG \\
\hline
\end{tabular}
\caption{Pepeheavyhash Token Details}
\end{table}

\subsection{Token Distribution}

The distribution of PEPEH tokens is designed to ensure fairness and promote wide participation in the ecosystem. The allocation is as follows:

\begin{table}[h]
\centering
\begin{tabular}{|l|r|l|}
\hline
\textbf{Allocation} & \textbf{Percentage} & \textbf{Amount (PEPEH)} \\
\hline
Public Minting & 70\% & 14,700,000,000 \\
Community Rewards & 15\% & 3,150,000,000 \\
Development Fund & 10\% & 2,100,000,000 \\
Team & 5\% & 1,050,000,000 \\
\hline
\textbf{Total} & \textbf{100\%} & \textbf{21,000,000,000} \\
\hline
\end{tabular}
\caption{Pepeheavyhash Token Distribution}
\end{table}

\subsection{Vesting Schedule}

To ensure long-term commitment and prevent market flooding, a vesting schedule is implemented for certain allocations:

\begin{itemize}
    \item \textbf{Public Minting (70\%)}: No vesting, available immediately upon minting.
    \item \textbf{Community Rewards (15\%)}: Released over 24 months, with a 6-month cliff.
    \item \textbf{Development Fund (10\%)}: Released over 36 months, with a 12-month cliff.
    \item \textbf{Team (5\%)}: Released over 48 months, with a 12-month cliff.
\end{itemize}

\subsection{Token Utility}

PEPEH tokens serve multiple purposes within the Pepeheavyhash ecosystem:

\begin{enumerate}
    \item \textbf{Governance}: Token holders can participate in decision-making processes.
    \item \textbf{Staking}: Users can stake tokens to earn rewards and participate in network security.
    \item \textbf{Transaction Fees}: PEPEH is used to pay for transaction fees on the network.
    \item \textbf{Access to Premium Features}: Certain features or services may require PEPEH tokens.
    \item \textbf{Community Rewards}: Active community members can earn PEPEH tokens.
\end{enumerate}

\subsection{Deflationary Mechanism}

To maintain token value over time, Pepeheavyhash implements a deflationary mechanism:

\begin{itemize}
    \item 1\% of all transaction fees are burned, permanently reducing the token supply.
    \item Quarterly buyback and burn events using a portion of the project's revenue.
\end{itemize}

\subsection{Token Issuance}

PEPEH tokens are minted through a fair and decentralized process:

\begin{itemize}
    \item Minting occurs on a first-come, first-served basis.
    \item Each address can mint a maximum of 1,000 PEPEH per transaction.
    \item A total of 10,000,000 minting transactions are allowed.
    \item Minting will cease once the public allocation of 14,700,000,000 PEPEH is exhausted.
\end{itemize}

This tokenomics model is designed to create a balanced and sustainable ecosystem for Pepeheavyhash, leveraging the unique features of the Kaspa network and the GhostDAG consensus mechanism to ensure scalability, efficiency, and fairness for all participants.

\section{Why Choose PEPEH?}
Pepeheavyhash brings a fresh and inspiring character to the KRC20 memecoin space, providing a new narrative and setting a new benchmark for memecoins on Kaspa \citep{memecoinfuture2024}. By joining the PEPEHEAVYHASH movement, you can help make the Kaspa ecosystem a fun and inclusive space for everyone while benefiting from the scalability, efficiency, and security of the groundbreaking GhostDAG consensus mechanism \citep{sompolinsky2020phantom}. Additionally, Pepeheavyhash promotes a positive message of health and wellness, encouraging a balanced lifestyle and personal growth \citep{cryptowellness2023}.

\section{Conclusion}
Pepeheavyhash is set to revolutionize the memecoin space on the Kaspa network, leveraging the innovative GhostDAG consensus mechanism for scalability, efficiency, and security \citep{sompolinsky2020phantom, kaspadev2024}. With its unique character and community-driven approach, it aims to inspire innovation, set new standards, and promote a positive message of health and wellness. Join us in this exciting journey and become part of the PEPEHEAVYHASH movement, contributing to the growth and adoption of the Kaspa network and its groundbreaking technology, while fostering a vibrant and inclusive community \citep{cryptocommunity2024}.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
